### 2019-03-14 Bucketing/intro.tex
Add citations
Also add the cite package so we can put multiple citations together

\emph{Theory exploration} (TE) describes an open-ended search for
interesting properties (conjectured or proven) of a given set of formal
definitions, such as a mathematical theory, a scientific model or a software
library. It has been applied to generating ``background lemmas'' in the
interactive proof assistant \textsc{Isabelle/HOL}~TODO{CITE ISACOSY AND HIPSTER}
and for automated theorem proving~TODO{CITE PAPER WHICH SHOWS IMPROVED PROVING},
as well as for generating specifications for (pure functional) programming
libraries~TODO{CITE QUICKSPEC 1, 2 AND SPECULATE}.

>>>>

\emph{Theory exploration} (TE) describes an open-ended search for
interesting properties (conjectured or proven) of a given set of formal
definitions, such as a mathematical theory, a scientific model or a software
library. It has been applied to generating ``background lemmas'' in the
interactive proof assistant
\textsc{Isabelle/HOL}~\cite{johansson2009isacosy,Hipster} and for automated
theorem proving~\cite{claessen2013automating}, as well as for generating
specifications for (pure functional) programming
libraries~\cite{QuickSpec,smallbone2017quick,braquehais2017speculate}.
